---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ggplot2)
summary(diamonds)
```

#### 钻石价格直方图
```{r}
ggplot(aes(x = price), data = diamonds) + 
  geom_histogram(binwidth = 200)
```


```{r}
diamonds[diamonds$price >= 15000,]
```

Explore the largest peak in the price histogram you created earlier.
Try limiting the x-axis, altering the bin width, and setting different breaks on the x-axis.

You can save images by using the ggsave() command.
ggsave() will save the last plot created.
For example...
                  qplot(x = price, data = diamonds)
                  ggsave('priceHistogram.png')

ggsave currently recognises the extensions eps/ps, tex (pictex), pdf, jpeg, tiff, png, bmp, svg and wmf (windows only).

```{r}
ggplot(aes(x = price), data = diamonds) + 
  geom_histogram(binwidth = 50) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))
ggsave('priceHistogram.png')
```
#### 切工-价格直方图

```{r}
ggplot(aes(x = price), data = diamonds) + 
  geom_histogram(binwidth = 100) + 
  scale_x_continuous(breaks = seq(0, 1000, 100)) +
  facet_wrap(~cut)
```

```{r}
table(diamonds$cut)
by(diamonds$price, diamonds$cut, summary)
```
#### 标尺和多直方图
http://www.cookbook-r.com/Graphs/Facets_(ggplot2)/
```{r}
ggplot(aes(x = price), data = diamonds) + 
  geom_histogram(binwidth = 100) + 
  scale_x_continuous(breaks = seq(0, 1000, 100)) +
  facet_wrap(~cut, scales="free_y")
```
#### 由切工决定的每克拉价格
提示 1：你可以在参数 x 中使用价格和克拉变量。什么表达式可使你得到每克拉价格？ 
提示 2：对于长尾分布，你可以添加一个 ggplot 图层（如：scale_x_log10()）来转换变量。
```{r}
library(gridExtra) 
ggplot(aes(x = price), data = diamonds) + 
  geom_histogram() + 
  facet_wrap(~cut, scales="free_y") +
  scale_x_log10()
  
```
#### 价格箱线图
在箱线图中，我们将 y 参数作为连续数据，将 x 参数作为分类数据。

```{r}
ggplot(aes(y = price), data = diamonds) + 
  geom_boxplot() + 
  facet_wrap(~cut, scales="free_y") +
  coord_cartesian()

```
#### 四分位数间距 — IQR
```{r}
IQR(subset(diamonds, price <1000)$price) 
```

```{r}
IQR(subset(diamonds, color =='D')$price)
```
```{r}
IQR(subset(diamonds, color =='J')$price)
```


```{r}
by(diamonds$price, diamonds$color, summary)
```

#### 由颜色表示的每克拉价格箱线图
```{r}
ggplot(aes(y = price/carat), data = diamonds) + 
  geom_boxplot(aes(color = color)) 
```

#### 克拉频率多边形
对于这个问题，我们寻找的是精确值的计数 — 尝试从较大的组宽开始，接着减小组宽，以查看图形是如何变化的，然后关注你最感兴趣的值。
```{r}
ggplot(aes(x = carat), data = diamonds) + 
  geom_freqpoly(binwidth=0.1) +
  scale_x_continuous(breaks = seq(0, 5, 0.5)) +
  scale_y_continuous(breaks = seq(0,10000,2000))
  

```
#### Gapminder 数据

The Gapminder website contains over 500 data sets with information about
the world's population. Your task is to download a data set of your choice
and create 2-5 plots that make use of the techniques from Lesson 3.

You might use a simple histogram, a boxplot split over a categorical variable,
or a frequency polygon. The choice is yours!

You can find a link to the Gapminder website in the Instructor Notes.

Once you've completed your investigation, create a post in the discussions that includes:
      1. any questions you answered, your observations, and summary statistics
      2. snippets of code that created the plots
      3. links to the images of your plots
```{r}

```

```{r}

```







































