---
output: html_document
editor_options: 
  chunk_output_type: inline
---
第 6 课
========================================================

### 欢迎语
注释：

***
```{r}
library(ggplot2)
data("diamonds")
```
### 散点图回顾 Scatterplot Review
Let's start by examining two variables in the data set.
The scatterplot is a powerful tool to help you understand the relationship between two continuous variables.

We can quickly see if the relationship is linear or not.
In this case, we can use a variety of diamond characteristics to help us figure out whether the price advertised for any given diamond is 
reasonable or a rip-off.

Let's consider the price of a diamond and it's carat weight.
Create a scatterplot of price (y) vs carat weight (x).

Limit the x-axis and y-axis to omit the top 1% of values.
```{r}
ggplot(aes(x = carat, y = price), data = diamonds) +
  geom_point() +
  xlim(0, quantile(diamonds$carat, 0.99)) +
  ylim(0, quantile(diamonds$price, 0.99))
```
```{r}
qplot(x = carat, y = price, data = diamonds) +
  geom_point(fill = '#F79420', color = 'black', shape = 21) +
  #geom_point(fill = I('#F79420'), color = I('black'), shape = 21) +也可
  xlim(0, quantile(diamonds$carat, 0.99)) +
  ylim(0, quantile(diamonds$price, 0.99)) 
  
```

***

### 价格与克拉的关系
回复：
```{r}
ggplot(aes(x = carat, y = price), data = diamonds) +
  geom_point(color = '#F79420', alpha = 1/10) +
  stat_smooth(method = 'lm') +
  xlim(0, quantile(diamonds$carat, 0.99)) +
  ylim(0, quantile(diamonds$price, 0.99))
```

***

### Frances Gerety
注释：

#### 钻石是

***

### 钻石的兴起
注释：

***

### ggpairs 函数 ggpairs Function
注释：
如有需要，安装下列组件
install.packages('GGally')
install.packages('scales')
install.packages('memisc')
install.packages('lattice')
install.packages('MASS')
install.packages('car')
install.packages('reshape2')

```{r}
# 加载 ggplot 图画组件及其他内容
library(GGally)
library(scales)
library(memisc)

# 数据集中 10,000 个钻石的样本
set.seed(20022012)
diamond_samp <- diamonds[sample(1:length(diamonds$price), 10000), ]
ggpairs(diamond_samp, 
        lower = list(continuous = wrap("points", shape = I('.'))), 
        upper = list(combo = wrap("box", outlier.shape = I('.'))))

```

```{r}
ggpairs(diamond_samp, 
        lower = list(continuous = wrap("points", shape = I('.'))), 
        upper = list(combo = wrap("box", outlier.shape = I('.'))),
        axisLabels ='internal')
```

在 ggpairs 输出中你发现了什么？
回复：

***

### 钻石的需求 The Demand of Diamonds
注释：
Create two histograms of the price variable and place them side by side on one output image.

The first plot should be a histogram of price and the second plot should transform the price variable using log10.

Set appropriate bin widths for each plot.
ggtitle() will add a title to each histogram. 

```{r}
library(gridExtra)

p1 <- qplot(data = diamonds, x = price, binwidth = 100, 
               fill = I('#099DD9')) + 
  ggtitle('Price')

p2 <- qplot(data = diamonds, x = price, binwidth = 0.01, 
               fill = I('#F79420')) +
  scale_x_log10()
  ggtitle('Price (log10)')
  
grid.arrange(p1, p2, ncol=2)

```

***

### 结合需求和价格的分布
注释：

***

### 改变散点图 Scatterplot Transformation

```{r}
qplot(x = carat, y = price, data = diamonds) +
  geom_point(fill = '#F79420', color = 'black', shape = 21) +
  #geom_point(fill = I('#F79420'), color = I('black'), shape = 21) +也可
  scale_y_log10() + 
  ggtitle('Price (log10) by Carat')
  #xlim(0, quantile(diamonds$carat, 0.99)) +
  #ylim(0, quantile(diamonds$price, 0.99)) 
```


### 创建一个新函数，改变变量 carat cuberoot transformation

```{r}
cuberoot_trans = function() trans_new('cuberoot', transform = function(x) x^(1/3),
                                      inverse = function(x) x^3)
```

#### 使用函数 cuberoot_trans
```{r Use cuberoot_trans}
ggplot(aes(carat, price), data = diamonds) + 
  geom_point() + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')
```

***

### 再次访问过度绘制
 Sort and Head Tables
```{r}
head(sort(table(diamonds$carat), decreasing = T))
head(sort(table(diamonds$price), decreasing = T))
```

 Overplotting Revisited
```{r}
ggplot(aes(carat, price), data = diamonds) + 
  geom_point(alpha = 1/5, size = 0.75, position = 'jitter') + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')
```

***

### 其他定性因素
注释：

***

### 价格 vs. 克拉与净度 Price vs. Carat and Clarity

改变下列代码。
```{r}
# 安装并加载 RColorBrewer 组件
library(RColorBrewer)
ggplot(aes(x = carat, y = price, color = clarity), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
    guide = guide_legend(title = 'Clarity', reverse = T,
                         override.aes = list(alpha = 1, size = 2))) + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')
```

***

### 净度与价格
回复：

***

### 价格 vs. 克拉与切工Price vs. Carat and Cut

改变下列代码。
```{r}
ggplot(aes(x = carat, y = price, color = cut), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'cut', reverse = T,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and cut')
```

***

### 切工与价格
回复：

***

### 价格 vs. 克拉与颜色 Price vs. Carat and Color

改变下列代码。
```{r}
ggplot(aes(x = carat, y = price, color = color), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'color', #去掉reverse = T,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and color')
```

***

### 颜色与价格
回复：

***

### R 中的线性模型
注释：

回复：

***

### 构建线性模型 Building the Linear Model
Notes:

```{r}
m1 <- lm(I(log(price)) ~ I(carat^(1/3)), data = diamonds)
m2 <- update(m1, ~ . + carat)
m3 <- update(m2, ~ . + cut)
m4 <- update(m3, ~ . + color)
m5 <- update(m4, ~ . + clarity)
mtable(m1, m2, m3, m4, m5)
```

注意，把切工增加到我们模型中，为什么不利于解释钻石价格的方差。
之前没有探讨过这个问题。

***

### 模型中的问题
视频注释：

Research:
(花时间解决模型的 2-4 个问题)
(应该花费 10 到 20 分钟完成)

回复：

***

### 更大更优的数据集 A Bigger, Better Data Set
Notes:

install.package('bitops')
install.packages('RCurl')
library('bitops')
library('RCurl')

diamondsurl = getBinaryURL("https://raw.github.com/solomonm/diamonds-data/master/BigDiamonds.Rda")
load(rawConnection(diamondsurl))


这里可以获取得到数据所使用的代码：
https://github.com/solomonm/diamonds-data

## 使用更大的钻石数据集构建模型 Building a Model Using the Big Diamonds Data Set
Your task is to build five linear models like Solomon did for the diamonds data set only this time you'll use a sample of diamonds from the diamondsbig data set.

Be sure to make use of the same variables (logprice, carat, etc.) and model 
names (m1, m2, m3, m4, m5).

To get the diamondsbig data into RStudio on your machine, copy, paste, and run the 
code in the Instructor Notes. There's 598,024 diamonds in this data set!

Since the data set is so large, you are going to use a sample of the 
data set to compute the models. You can use the entire data set on your machine which 
will produce slightly different coefficients and statistics for the models.


```{r }
load("BigDiamonds.rda")
```
```{r}
diamondsbig$logprice = log(diamondsbig$price)
m1 <- lm(logprice ~ I(carat^(1/3)),
         data = diamondsbig[diamondsbig$price < 10000 &
                              diamondsbig$cert == 'GIA',])
m2 <- update(m1, ~ . + carat)
m3 <- update(m2, ~ . + cut)
m4 <- update(m3, ~ . + color)
m5 <- update(m4, ~ . + clarity)
mtable(m1, m2, m3, m4, m5)
```

***

## 预测

BlueNile 钻石例子：
直径为 1.00 等级很好 I VS I 的钻石价格是 $5,601
```{r}
head(diamondsbig)
```


```{r}
# 确保你已经加载了 memisc 库，保存为 m5 作为工作区的对象。
thisDiamond = data.frame(carat = 1.00, cut = "V.Good",
                         color = "I", clarity="VS1")

```
```{r}
modelEstimate = predict(m5, newdata = thisDiamond,
                        interval="prediction", level = .95)
exp(modelEstimate)
```

```{r}
dat = data.frame(m4$model, m4$residuals) 

with(dat, sd(m4.residuals)) 

with(subset(dat, carat > .9 & carat < 1.1), sd(m4.residuals)) 

dat$resid <- as.numeric(dat$m4.residuals)
ggplot(aes(y = resid, x = round(carat, 2)), data = dat) + 
  geom_line(stat = "summary", fun.y = sd) 
```

评估模型如何较好地预测 BlueNile 钻石价格。思考最佳点估计和 95% 的置信区间。

***

## 最终思考
注释：

***

点击 **KnitHTML** 查看你的成果和这节课的 html 页面、
答案和注释！
