---
title: "practice5"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data("diamonds")
library(ggplot2)
```
### 带有分面和颜色的价格直方图
```{r}
ggplot(aes(x = price), data = diamonds) + 
  geom_histogram(binwidth = 200, aes(color = cut)) +
  #scale_fill_brewer(type = 'qual', palette = 1) +
  facet_wrap(~color) 
```

```{r}
ggplot(aes(x = price, fill = cut), data = diamonds) + 
  #geom_histogram(binwidth = 500) + 如果用了binwidth，在加Scale_x_log10()有问题
  geom_histogram(bins = 40) +
  scale_fill_brewer(type = 'qual') +
  scale_x_log10() +
  facet_wrap(~color) 
```
```{r}
ggplot(aes(x = price, fill = cut), data = diamonds)+
  geom_histogram(bins = 35, position = position_stack(reverse = TRUE)) +
  scale_x_log10() +
  facet_wrap(~color, ncol = 3) +
  scale_fill_brewer(type ='qual')
```

### 价格与按切工填色的表格
Create a scatterplot of diamond price vs.table and color the points by the cut of
 the diamond.



```{r}
ggplot(aes(x=table,y=price),data=diamonds)+ #不用aes(x=table,y=price,fill=cut)，点无fill
  geom_point(aes(color=cut))+
  scale_color_brewer(type = 'qual')+
  scale_x_continuous(breaks=seq(50,80,2), lim=c(50,80))
```
### 价格与体积和钻石净度
Create a scatterplot of diamond price vs.volume (x * y * z) 
and color the points by the clarity of diamonds. 
Use scale on the y-axis to take the log10 of price. 
You should also omit the top 1% of diamond volumes from the plot.

Note: Volume is a very rough approximation of
a diamond's actual volume.


```{r}
diamonds$volume <- diamonds$x * diamonds$y * diamonds$z
ggplot(aes(x = volume, y = price, color = clarity), data = diamonds) +
  geom_point() +
  xlim(0, quantile(diamonds$volume, 0.99)) +
  #ylim(quantile(diamondsprice,0),quantile(diamondsprice, .99)) +
  scale_color_brewer(type = 'div', direction = -1)
```

```{r}
diamonds$volume <- diamonds$x * diamonds$y * diamonds$z
ggplot(aes(x = volume, y = price, color = clarity), data = diamonds) +
  geom_point() + 
  xlim(0, quantile(diamonds$volume, 0.99)) +
  scale_y_log10() +
  scale_color_brewer(type = 'div', direction = -1)
```

```{r}
diamonds$volume <- diamonds$x * diamonds$y * diamonds$z
ggplot(aes(x = volume, y = price, color = clarity), data = diamonds) +
  geom_point(position = position_stack(reverse = TRUE)) + #用直方图改图例顺序的方法不行
  xlim(0, quantile(diamonds$volume, 0.99)) +
  scale_y_log10() +
  scale_color_brewer(type = 'div', direction = -1)
```

```{r}
diamonds$clarity <- factor(diamonds$clarity, levels=rev(levels(diamonds$clarity)))
ggplot(aes(x = volume, y = price, color = clarity), 
       data = subset(diamonds, volume >0)) +
  geom_point() + 
  xlim(0, quantile(diamonds$volume, 0.99)) +
  ylim(0, quantile(diamonds$price, 0.99)) +
  scale_y_log10() +
  coord_cartesian(xlim =c(0,300))+ #你将可视化绘制再纸上之后，将纸裁剪成你要的大小。
  scale_color_brewer(type = 'div', direction = -1)
```
### 新建友谊的比例
Many interesting variables are derived from two or more others.
For example, we might wonder how much of a person's network on a service like Facebook the user actively initiated. 
Two users with the same degree (or number of friends) might be very different if one initiated most of those connections on the service, while the other initiated very few. 
So it could be useful to consider this proportion of existing friendships that
the user initiated. 
This might be a good predictor of how active a user is compared with their peers, or other traits, such as personality (i.e., is this person an extrovert?).
```{r}
pf = read.delim('pseudo_facebook.tsv')
pf$prop_initiated <- pf$friendships_initiated/pf$friend_count
```

下面这个应该也行
```{r}
pf$prop_initiated<- ifelse(pf$friend_count>0, pf$friendships_initiated/pf$friend_count,NA)
```
### prop_initiated 与使用时长
Create a line graph of the median proportion of friendships initiated ('prop_initiated') vs. tenure and color the line segment by year_joined.bucket.

Recall, we created year_joined.bucket in Lesson 5 by first creating year_joined from the variable tenure.
Then, we used the cut function on year_joined to create four bins or cohorts of users.

(2004, 2009]
(2009, 2011]
(2011, 2012]
(2012, 2014]

The plot should look something like this.
http://i.imgur.com/vNjPtDh.jpg
OR this
http://i.imgur.com/IBN1ufQ.jpg
```{r}
pf$year_joined <- floor(2014 - pf$tenure/365)
summary(pf$year_joined)
table(pf$year_joined)
```

```{r}
pf$year_joined.bucket <- cut(pf$year_joined, 
                             c(2004, 2009, 2011, 2012, 2014))
table(pf$year_joined.bucket)
```

```{r}
ggplot(aes(x = tenure, y = prop_initiated),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket))
```

```{r}

ggplot(pf, aes(x=tenure, y=prop_initiated, color=year_joined.bucket)) +
    geom_line(stat='summary', fun.y=median, na.rm=TRUE)
```
###平滑化 prop_initiated 与使用时长
Smooth the last plot you created of of prop_initiated vs tenure colored by
year_joined.bucket. 
You can bin together ranges of tenure or add a smoother to the plot.

There won't be a solution image for this exercise.
You will answer some questions about your plot in the next two exercises.

### 最大的 prop_initiated 组
平均来说，哪个组发起的 Facebook 好友请求比例最大？你在上个练习中创建的带平滑器的图可以帮你回答这个问题。 
○ 在 2009 年之前加入的人 
○ 在 2009 年至 2011 年之间加入的人
○ 在 2011 年至 2012 年之间加入的人 
○ 在 2012 后加入的人
```{r}
with(subset(pf, year_joined.bucket == '(2012,2014]'), summary(prop_initiated))
```
### 经过分组、分面和填色的价格/克拉
Create a scatter plot of the price/carat ratio of diamonds. 
The variable x should be assigned to cut. 
The points should be colored by diamond color, and the plot should be faceted by clarity.

The plot should look something like this.
http://i.imgur.com/YzbWkHT.jpg.

Note:  
In the link, a color palette of type 'div' was used to color the histogram using
scale_color_brewer(type = 'div')
```{r}
ggplot(aes(x = cut, y = price/carat), data = diamonds) +
  geom_point(aes(color=color)) +
  geom_jitter(aes(color=color)) +
  facet_wrap(~clarity) +
  scale_color_brewer(type = 'div')

```

```{r}
#diamonds$clarity <- factor(diamonds$clarity, levels=rev(levels(diamonds$clarity)))
#diamonds$cut <- factor(diamonds$cut, levels=rev(levels(diamonds$cut)))
ggplot(aes(x = cut, y = price/carat), data = diamonds) +
  geom_point(aes(color=color)) +
  geom_jitter(aes(color=color)) +
  facet_wrap(~clarity) +
  scale_color_brewer(type = 'div')
```
### Gapminder 多变量分析
The Gapminder website contains over 500 data sets with information about
the world's population. Your task is to continue the investigation you did at the
end of Problem Set 4 or you can start fresh and choose a different
data set from Gapminder.

If you’re feeling adventurous or want to try some data munging see if you can
find a data set or scrape one from the web.

In your investigation, examine 3 or more variables and create 2-5 plots that make
use of the techniques from Lesson 5.

You can find a link to the Gapminder website in the Instructor Notes.

Once you've completed your investigation, create a post in the discussions that includes:
      1. the variable(s) you investigated, your observations, and any summary statistics
      2. snippets of code that created the plots
      3. links to the images of your plots
```{r}

```


